### 2019-01-16 thesis_report/methods.tex
changed alpha max to alpha min

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.75\columnwidth]{images/zigzag.pdf}
		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
		\label{fig:setup}}
		\end{figure}

@@

		\comment{We first link the long trajectories to a maximum allowed angle.}
		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$$ axis.
		By defining a minimum angle, we thus can filter out the long trajectories.
		We define this angle by identifying the angle

>>>>

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.75\columnwidth]{images/zigzag_methods.pdf}
		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
		\label{fig:setup}}
		\end{figure}

@@

		\comment{We first link the long trajectories to a maximum allowed angle.}
		In the infinite system, the long trajectories have a small angle with respect to the $x^\prime$ axis.
		By defining a minimum angle, we thus can filter out the long trajectories.
		We define this angle by identifying it with the angle of the longest trajectory from one side of the superconductor to the other.
